Reformulating phylogenetic mixed models to improve flexibility and speed

### 2018-11-06 phyloglmm_ms.tex
updated figures

\begin{center}
\begin{figure}[h]
  \includegraphics[scale=0.8,page=1]{./git_push/plot.Rout.pdf}
  \caption{New}
\label{ssplot}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[h]
  \includegraphics[scale=0.8,page=2]{./git_push/plot.Rout.pdf}
  \caption{New}
\label{ssplot}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[h]
  \includegraphics[scale=0.8,page=3]{./git_push/plot.Rout.pdf}
  \caption{New}
\label{ssplot}
\end{figure}
\end{center}

@@

\begin{center}
\begin{figure}[h]
  \includegraphics[scale=0.8,page=4]{./git_push/plot.Rout.pdf}
  \caption{new}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[h]
  \includegraphics[scale=0.8,page=6]{./git_push/plot.Rout.pdf}
  \caption{new}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[h]
  \includegraphics[scale=0.8,page=7]{./git_push/plot.Rout.pdf}
  \caption{new}
\end{figure}
\end{center}

>>>>

\begin{center}
\begin{figure}[h]
  \includegraphics[scale=0.8,page=1]{./figure/ssplot.pdf}
  \caption{New}
\label{ssplot}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[h]
  \includegraphics[scale=0.8,page=1]{./figure/sstime.pdf}
  \caption{New}
\label{ssplot}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[h]
  \includegraphics[scale=0.8,page=1]{./figure/sscoverage.pdf}
  \caption{New}
\label{ssplot}
\end{figure}
\end{center}

@@

\begin{center}
\begin{figure}[h]
  \includegraphics[scale=0.8,page=1]{./figure/msplot.pdf}
  \caption{new}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[h]
  \includegraphics[scale=0.8,page=1]{./figure/mstime.pdf}
  \caption{new}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[h]
  \includegraphics[scale=0.8,page=1]{./figure/mscoverage.pdf}
  \caption{new}
\end{figure}
\end{center}
